\propertitle

### 2019-12-06 maxNt_v6.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-06T11:13:57+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Inferring the total activity of a large neuronal population\\ from a small sample}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

\section{Introduction:\\a simple model for questions about large neuronal
  populations}
\label{sec:intro}

@@

Answering this kind of questions always engages an element of uncertainty.
We cannot say \enquote{the answer is such and such}; at best we can assign
degrees of reasonable belief -- that is, probabilities -- to the possible
answers. The assessment of this distribution of belief involves
experimental data, such as recordings of neuronal activity from specific
brain areas, and pre-data knowledge about biological conditions and
mechanisms. Our pre-data \dobs\ are often simplified, to be mathematically
tractable, and are therefore called \enquote{models}.

@@

\mynote{[Yasser:] In the present work we aim to address the issue of
  building probability distributions over a large population using
  recording from subpopulations by considering the distribution of total
  population activity as an example. [} In the present work we propose such
an intermediate probability model. It answers this question: How much was
the \emph{total} activity of a large neuronal population, given the
observation of the activity of a very small sample thereof? This model
addresses a larger brain area, avoiding the assumption of isolation of the
sample; and by focusing on the total activity, rather than the activity of
individual neurons, it remains simple and numerically tractable.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-06T11:26:19+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Inferring the total activity of a large neuronal population\\ from a small sample}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

\section{Introduction:\\a model for questions about large neuronal
  populations}
\label{sec:intro}

@@

Answering this kind of questions always engages an element of uncertainty.
We cannot say \enquote{the answer is such and such}; at best we can assign
degrees of reasonable belief -- that is, probabilities -- to the possible
answers. The assessment of such distributions of belief involves
experimental data, such as recordings of neuronal activity from specific
brain areas, and pre-data knowledge and assumptions about biological
conditions and mechanisms. Our pre-data \dobs\ are often simplified, to be
mathematically tractable, and are therefore called \enquote{models}.

@@

% \mynote{[Yasser:] In the present work we aim to address the issue of
%   building probability distributions over a large population using
%   recording from subpopulations by considering the distribution of total
%   population activity as an example. [} 
In the present work we propose such
an intermediate probability model. It answers this question: How much was
the \emph{total} activity of a large neuronal population, given the
observation of the activity of a very small sample thereof? This model
addresses a larger brain area, avoiding the assumption of isolation of the
sample; and by focusing on the total activity, rather than the activity of
individual neurons, it remains simple and numerically tractable.
